Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-09 R0V0.tex
Rewrite the neighbor case in the example

In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. The sets $\mathbf{C}_j$, $j\in\mathbb{N}_{[1,8]}$, are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}_1=\mathbf{C}_2=\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top
	\end{array} 
\end{equation*}

\todo[inline]{From here}

For each

Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience, $q_0:=q_1$ and $q_5:=q_4$).

>>>>

In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. The sets $\mathbf{C}_j$, $j\in\mathbb{N}_{[1,8]}$, are defined as
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}1, 1, 1, 0\end{bmatrix}^\top\right\},\\
		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0, 1, 1, 1\end{bmatrix}^\top\right\},&		    \mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0, 0, 1, 1\end{bmatrix}^\top\right\}\;.
	\end{array} 
\end{equation*}

The sets $\mathbf{X}(\mathscr{K}(\cdot))$ are defined as $\mathbf{X}(\mathscr{K}(1))=\{q_1,q_2\}$,  $\mathbf{X}(\mathscr{K}(2))=\{q_1,q_2,q_3\}$, $\mathbf{X}(\mathscr{K}(3))=\{q_2,q_3,q_4\}$ and $\mathbf{X}(\mathscr{K}(4))=\{q_3,q_4\}$.
